refractory erectile dysfunction (by ArticleAggregator_v05)

### 2023-02-22 ArticleAggregatorCS.qmd
PubMed fail even with new APIkey

## Manually input missing values ;)
```
## Pubmed
```{r}
#| label: PubMed connection and article extraction
api_key <- "0b1204719f054732c66e608d9d3f2c749c08"

>>>>

## Manually input missing values ;)
```
## Pubmed
```{r}
#| label: PubMed connection and article extraction
# api_key <- "0b1204719f054732c66e608d9d3f2c749c08"
api_key <- "7677957ef60aa19aa6c5856e126b696d6408"
